\begin{thebibliography}{8}
\bibitem{b1} Nakamoto, S. : Bitcoin: A peer-to-peer electronic cash system (2008). 
\bibitem{b2} Rosenfeld, M. : Analysis of bitcoin pooled mining reward systems. arXiv preprint arXiv:1112.4980 (2011).
\bibitem{b3} Bag, S., Sakurai, K. : Yet another note on block withholding attack on bitcoin mining pools. In: Bishop M., Nascimento A. (eds) Information Security. ISC 2016, LNCS, vol. 9866, pp. 167-180. Springer, Cham, Honolulu (2016).  
\bibitem{b4} Kwon, Y., Kim, D., Son, Y., Vasserman, E., Kim, Y : Be selfish and avoid dilemmas: Fork after withholding (faw) attacks on bitcoin. In: Proceedings of the 2017 ACM SIGSAC Conference on Computer and Communications Security, pp. 195-209. ACM, Dallas (2017).
\bibitem{b5} Eyal, I. : The miner's dilemma. In: Security and Privacy (SP), 2015 IEEE Symposium on, pp. 89-103. IEEE, San Jose (2015).  
\bibitem{b6} Luu, L., Saha, R., Parameshwaran, I., Saxena, P., Hobor, A. : On power splitting games in distributed computation: The case of bitcoin pooled mining. In: Computer Security Foundations Symposium (CSF), 2015 IEEE 28th, pp. 397-411. IEEE, Verona (2015). 
\bibitem{b7} Schrijvers, O., Bonneau, J., Boneh, D., Roughgarden, T. : Incentive compatibility of bitcoin mining pool reward functions. In: Grossklags J., Preneel B. (eds) Financial Cryptography and Data Security. FC 2016, LNCS, vol. 9603, pp. 477-498. Springer, Berlin, Heidelberg (2016). 
\bibitem{b8} Eyal, I. and Sirer, E.G. : Majority is not enough: Bitcoin mining is vulnerable. Communications of the ACM \textbf{61} (7), 95-102 (2018).
\bibitem{b9} Nayak, K., Kumar, S., Miller, A., Shi, E. : Stubborn mining: Generalizing selfish mining and combining with an eclipse attack. In: Security and Privacy (EuroS\&P), 2016 IEEE European Symposium on, pp. 305-320. IEEE, Saarbr{\"u}cken (2016).    
\bibitem{b10} Selfish Mining: A 25\% Attack Against the Bitcoin Network. \url{https://bitcoinmagazine.com/articles/selfish-mining-a-25-attack-against-the-bitcoin-network-1383578440/}. Last accessed 11 Sep 2018.
\bibitem{b11} Zhang, R., Preneel, B. : Publish or Perish: A Backward-Compatible Defense against Selfish Mining in Bitcoin. In: Handschuh H. (eds) Topics in Cryptology – CT-RSA 2017, LNCS, vol. 10159, pp. 277-292. Springer, Cham, San Francisco (2017).  
\bibitem{b12} Hashrate Distribution. \url{https://www.blockchain.com/en/pools}. Last accessed 10 Sep 2018.  


\end{thebibliography}